---
title: "Ebola Surveillance"
author: Philipp Ross
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
    toc: true
    highlight: pygments
---

This report connects with the homework for units 7, 8, 9, and 10. I'll be looking to recreate a small piece of the analysis done in Gire et al. 2014 where I look at ebola isolates sampled at different time points during 2014 to see if I can differentiate them by their variant calls.

Collection Dates and Accessions:

* May 28th    - `SRR1553468`
* July 8th    - `SRR1972721`
* August 20th - `SRR1735146`

That information can be found [here](http://www.ncbi.nlm.nih.gov/Traces/study/?acc=SRP045416).

The reference genome I'll be comparing these samples to is the assembly in Figure 4 of Gire et al. 2014, the Kissidougou Guinean sequence (accesion KJ660346).

```{r child = 'homework7.Rmd'}
```

```{r, echo = F}
rmarkdown::render("homework7.Rmd")
```

```{r child = 'homework8.Rmd'}
```

```{r, echo = F}
rmarkdown::render("homework8.Rmd")
```

```{r child = 'homework9.Rmd'}
```

```{r, echo = F}
rmarkdown::render("homework9.Rmd")
```

```{r child = 'homework10.Rmd'}
```

```{r, echo = F}
rmarkdown::render("homework10.Rmd")
```